Flexibility of interactions depends on habitat suitability

### 2019-09-13 paper/manuscript.Rmd
Fix legend for random plot so that it shows number of species included in the plot a
add median suitability per community figure to manuscript

After performing our sensitivity analysis, we found that we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.

@@

@@

n_random_pla <- n_random_species %>%
  dplyr::filter(guild == "pla_id")

n_random_ani <- n_random_species %>%
  dplyr::filter(guild == "ani_id")

>>>>

After performing our sensitivity analysis, we found that we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
When inspecting the suitability values of the analysed species we found that some communitues have larger overal suitability values. 
However, most communities included species for which habitat suitability was low and species for which it was high (Fig. \@ref(fig:fig-median-suitability)).

@@

```{r fig-median-suitability, fig.width = width('single'), fig.height = 2.2*1.5, fig.cap = "Median habitat suitability of communities in our dataset. Each row represents a different community and horizontal lines represent span the 2.5 and 97.5 quantiles."}
readd(fig_median_suitability)
```

@@

n_random_pla <- n_random_species %>%
  dplyr::filter(guild == "pla_id") %$%
  n_sp

n_random_ani <- n_random_species %>%
  dplyr::filter(guild == "ani_id") %$%
  n_sp
